Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-07-27 paper/paper-nature-revised.tex
minor editorial revisions

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{July 6, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, \textbf{formally
known as Hansard\textsuperscript{1},} plays a fundamental role in
capturing the history of political proceedings and facilitating the
exploration of valuable research questions. Originating in the British
parliament, the production of Hansard became tradition in many other
Commonwealth countries, such as Canada and Australia\textsuperscript{2}.
Given the content and magnitude of these records, they have
significance, particularly in the context of political science research.
In the case of Canada, the Hansard has been digitized for 1901 to
2019\textsuperscript{3}. Having a digitized version of Hansard enables
researchers to conduct text analysis and statistical modelling.
Following the lead of that project, in this paper we introduce a similar
database for Australia. This is composed of individual datasets for each
sitting day in the House of Representatives from 1998 to
\textbf{September} 2022, containing details on everything said in
parliament in a form that can be readily used by researchers. With the
development of tools for large-scale text analysis, this database will
serve as a resource for understanding political behaviour in Australia
over time.

\textbf{There are a wide variety of potential applications of this
database. For instance, within Australia there is considerable concern
that there has been a decline in the `quality' of public policy debate
(however that might be defined). Our dataset could be used to look at
whether it is really getting worse in particular ways, and if so, why.
We might also be interested in whether particular sub-populations are
appropriately represented in what is talked about in parliament. For
instance, there is often concern that regional areas are overlooked
compared with metropolitan areas. Again, our database could be used to
examine whether this has changed over time. We have developed our
database in such a way that it could be linked with similar databases
from other countries which would enable comparative analysis. For
instance, we may be interested in how the policy focus of a parliament
changes given various global events such as pandemics or wars. An
international linkage provides a comparison case where domestic issues
are different while international ones are common. As an example of
enabling this linkage we have included PartyFacts IDs in our database.
This should make it possible to link our database with other large
parliamentary speech collection projects, such as
ParlaMint\textsuperscript{4}, ParlSpeech\textsuperscript{5},
ParlEE\textsuperscript{6}, and MAPLE\textsuperscript{7}.}

@@

At present, the Hansard format that is available on the Parliament of
Australia website is not easily accessible for large scale analysis. To
this point, various researchers have had to create their own databases
of usable, complete data based on content from the Australian Parliament
website. For instance, an online, easy to read database of Hansard from
1901 to 1980 using the XML files has been created\textsuperscript{9}.
These data can be navigated by year, parliament, people, and
bills\textsuperscript{9}. To make the Australian Parliamentary Handbook
more accessible, an \texttt{R} package which includes data on all MPs
from 1945 to 2019 has been created\textsuperscript{10}. Further, there
is the \texttt{AustralianPoliticians} \texttt{R} package, which contains
several datasets related to the political and biographical information
of Australian federal politicians who were active between 1901 and
2021\textsuperscript{11}. \textbf{And finally, there has been
examination of speech and MP level data between 1990 and 2019 in
Australia\textsuperscript{12}. Like us they scrape the Hansard record
and link it with biographical data. The key difference is that our focus
is on the database itself, while they are focused on using a database
constructed from the same source to answer a particular question about
speaker time. This different focus leads to different emphasis and
approaches.}

@@

This section is structured as follows. First, we provide an overview of
our approach to understanding and parsing an individual Hansard XML
document, which informed the scripts used to create our database. This
will be supplemented with an excerpt from a Hansard XML to provide a
visual example of its structure. Next we will explain the specific
differences between the scripts, and outline what structural changes
necessitated their separate development. We then provide details on the
methodological intricacies of three core components of Hansard
proceedings: Question Time, interjections, and stage directions.
Further, we discuss the script we developed to fill in remaining missing
details on the MP speaking, which each file in our database was passed
to after being parsed and cleaned. \textbf{Finally, we review the
supplementary Hansard debate topics dataset and supplementary divisions
dataset we created to expand the versatility of our database.}

@@

The outer-most node, also known as the parent node, is denoted
\texttt{\textless{}hansard\textgreater{}} and serves as a container for
the entire document. This parent node may have up to four child nodes,
where the first child node contains details on the specific sitting day.
Next, \texttt{\textless{}chamber.xscript\textgreater{}} contains all
proceedings of the Chamber,
\texttt{\textless{}fedchamb.xscript\textgreater{}} contains all
proceedings of the Federation Chamber, and
\texttt{\textless{}answers.to.questions\textgreater{}} contains Question
Time proceedings. The Federation Chamber does not meet on every sitting
day, so this child element is not present in every XML file. The use of
separate child nodes allows for the distinction of proceedings between
the Chamber and Federation Chamber. The structure of the
\texttt{\textless{}chamber.xscript\textgreater{}} and
\texttt{\textless{}fedchamb.xscript\textgreater{}} nodes are generally
the same, where the proceeding begins with
\texttt{\textless{}business.start\textgreater{}} which is followed by a
series of debates. Debate nodes can contain a
\texttt{\textless{}subdebate.1\textgreater{}} child node which has a
\texttt{\textless{}subdebate.2\textgreater{}} child node nested within
it. That said, sometimes \texttt{\textless{}subdebate.2\textgreater{}}
is not nested within \texttt{\textless{}subdebate.1\textgreater{}}. Each
of these three elements (i.e.~\texttt{\textless{}debate\textgreater{}},
\texttt{\textless{}subdebate.1\textgreater{}}, and
\texttt{\textless{}subdebate.2\textgreater{}}) as well as their
respective sub-elements contain important information on the topic of
discussion, who is speaking, and what is being said. The
\texttt{\textless{}speech\textgreater{}} node within each one contains
the bulk of the text associated with that debate or sub-debate. A
typical \texttt{\textless{}speech\textgreater{}} node begins with a
\texttt{\textless{}talk.start\textgreater{}} sub-node, providing
information on the MP whose turn it is to speak and the time of their
first statement. Unsurprisingly, speeches rarely go uninterrupted in
parliamentary debate settings --- they are often composed of a series of
interjections and continuations. These statements are categorized under
different sub-nodes depending on their nature, such as
\texttt{\textless{}interjection\textgreater{}} or
\texttt{\textless{}continuation\textgreater{}}. The final key component
of Hansard is Question Time, in which questions and answers are
classified as unique elements. More detail on the purpose and processing
of Question Time will follow in Section~\ref{sec-qa}.

@@

{\centering \includegraphics{xml1.png}

@@

The next step was to further develop our script to produce tidy data
sets, as defined and introduced by\textsuperscript{19}. These contain
all parsed text elements, where each statement is separated onto its own
row with details about the MP who is speaking, and rows are maintained
in chronological order. This first involved correcting the variable
classes and adding several indicator variables to differentiate where
statements came from, such as Chamber versus Federation Chamber or
\texttt{\textless{}subdebate.1\textgreater{}} versus
\texttt{\textless{}subdebate.2\textgreater{}}. The next key task stemmed
from the fact that the raw text data were not separated by each
statement when parsed. In other words, any interjections, comments made
by the Speaker or Deputy Speaker and continuations within an individual
speech were all parsed together as a single string. As such, the name,
name ID, electorate and party details were only provided for the person
whose turn it was to speak. There were many intricacies in the task of
splitting these speeches in a way that would be generalizable across
sitting days. Details on these are provided in
Section~\ref{sec-interject}.

@@

Once the script ran without error for a few recent years of Hansard, we
continued to work backwards until extensive changes in tree structure
made our script incompatible with parsing earlier XML files. The
earliest sitting day this first script can successfully parse is 14
August 2012. Before developing new scripts to parse earlier Hansard
documents, we prioritized cleaning and finalizing what we had been able
to parse. As such we continued building our script, fixing any problems
we noticed in the resulting datasets such as excess whitespace or
spacing issues, and splitting up any additional sections of the parsed
text onto separate rows where necessary. Specifically, we added a
section of our script to separate out general stage directions. More
information on this separation will be provided in
Section~\ref{sec-stage}. After completing our first script, it was
formatted as a function which takes a single file name argument and
produces one CSV file containing data on all proceedings from the given
sitting day.

@@

As mentioned, we developed a total of four scripts to parse the
1998-2022 time frame of Hansard documents. Two main factors motivated us
to create four scripts as opposed to just one, the first being
structural variation in XML over time, and the second being improved
computational efficiency with separate scripts. While all four scripts
use the same general approach to parsing described in
Section~\ref{sec-overview} and produce the same CSV structure, the first
and second scripts use a different method of data processing than the
third and fourth scripts.

@@

{\centering \includegraphics[width=3.28125in,height=\textheight]{patternEX.png}

@@

We then added binary flags to differentiate between questions and
answers. To do this in the first and second scripts, we separately
re-parsed question and answer content using the XPath expressions
\texttt{"chamber.xscript//question"} and
\texttt{"chamber.xscript//answer"}, added the correct question and
answer flags accordingly, and then added those flags back to the main
dataframe based on exact text matches. For the third and fourth scripts,
we made use of the fact that the patterns preceding text transcribed
under a question node were stored separately from those transcribed
under an answer node. As a result, we could readily use those patterns
to flag questions and answers correctly based on which list of patterns
it belonged to. Sometimes, \textbf{we identified} questions
\textbf{which} were incorrectly transcribed under an answer node and
vice-versa, in which cases we manually corrected the question and answer
flags. For instance, we check for any statements flagged as questions
which include the phrase ``has provided the following answer to the
honourable member's question'', in which case we re-code that statement
as an answer. \textbf{It is important to note, however, that because we
identified and corrected for these transcription errors manually as we
discovered them, additional flagging errors may exist which we did not
catch. As such, users may identify and should be wary of occasional
incorrectly flagged questions or answers in the data.}

@@

As mentioned in Section~\ref{sec-diff}, more recent years of Hansard
XMLs contain a series of child nodes which exist to capture the
structure of interruptions in that speech. Figure~\ref{fig-xml3}
provides an example of this, where the speech was interrupted by a
comment from the Deputy Speaker, and then the MP continued their speech.
Looking at the element names highlighted in blue, these child nodes do
not contain the actual text for the interjection or continuation ---
this text is embedded within the speech above it. However, as shown by
the content highlighted in pink in Figure~\ref{fig-xml3}, we were able
to extract useful details on the individual interjecting which we could
use later. Making use of this structure, we extracted names and
information of all individuals that were categorized within the XML as
interjections. We stored this as a dataframe called
\texttt{"interject"}. We decided not to include this data in our final
database, as it is embedded in our resulting datasets which have a flag
for interjections.

@@

{\centering \includegraphics[width=3.59375in,height=\textheight]{xml3.png}

@@

\caption{\label{fig-xml3}Snapshot of XML structure with interjection and
continuation from 03 February 2021 Hansard}

@@

We then created lists using both the \texttt{interject} and
\texttt{main} dataframes to capture all the names of individuals who
spoke that day. We added the names of all MPs in a number of unique
formats, due to the frequent variation in how names are transcribed in
Hansard. When an MP interjects or continues a speech, the usual form of
their name is a title followed by their first name or first initial
and/or last name. There is also variation in the capitalization of these
names.\footnote{Sometimes when someone's first name is included, only
  their last name is capitalized, while sometimes their full name is
  capitalized, or other times neither are capitalized.} Another source
of variation is in individuals with more than one first name, as
sometimes only their initial first name is written, while other times
their entire first name is written. Additionally, some surnames have
punctuation, and some surnames have specific capitalization such as
``McCormack'', where even in full capitalization, the first ``c''
remains lower case. This variation demands careful consideration when
writing regular expression patterns. In these lists we also accounted
for any general interjection statements that were not attributed to an
individual, such as ``An opposition member interjecting-''.

@@

{\centering \includegraphics[width=4.66667in,height=\textheight]{lookup_ex.png}

@@

{\centering \includegraphics{interject_ex.png}

@@

Having developed a successful methodology for splitting interjections,
we used this to inform our general approach in the third and fourth
scripts. However, the difference in data cleaning used in these scripts
necessitated some departure from the original methodology. As discussed
in Section~\ref{sec-diff}, we used string patterns extracted from
\texttt{\textless{}talk.start\textgreater{}} nodes to separate speeches.
As evident in Figure~\ref{fig-xml3},
\texttt{\textless{}talk.start\textgreater{}} nodes are nested within
\texttt{\textless{}interjection\textgreater{}} nodes, meaning that the
patterns of data from interjection statements were separated out in the
process. In other words, our approach to data cleaning in the third and
fourth scripts separated out interjections in the process. This meant
that we did not need to create lists of names and titles for which to
search in the text as we did before. However, we used the same list of
general interjection statements on which to separate as was used in the
first two scripts. We then did an additional check for statements that
may have not been separated due to how they were embedded in the XML,
and separated those out where needed.\footnote{While most statements
  were categorized in their own child node and hence captured through
  pattern-based separation, some were not individually categorized, and
  had to be split manually in this step.}

@@

{\centering \includegraphics{pattern_lookup.png}

@@

When building our first scripts, one of the final components needed was
to separate general stage directions out from statements made by MPs.
Stage directions are general statements included in the transcript to
document happenings in parliament. Examples of stage directions are
``Bill read a second time'', ``Question agreed to'', or ``Debate
adjourned''. It was unclear to us from the XML and PDF who exactly these
statements were attributed to. For further clarification, we watched
portions of the video recording for some sitting days, and noticed that
while these statements are documented in Hansard, they are not
explicitly stated in parliament. For example, when the Deputy Speaker
says ``The question is that the bill be now read a second time'', MPs
vote, and if the majority is in favour, they proceed reading the bill
the second time. This vote and second reading is not explicitly
transcribed, rather what is written is: ``Question agreed to. Bill read
a second time''. For this reason, we filled the name variable for these
statements with ``stage direction''. Stage directions were not flagged
as interjections. These stage directions are not defined differently
from the regular debate speech in the XML, meaning we had to manually
create a list of stage directions to separate out of the speeches. We
built this list of stage directions as we worked backwards in parsing
Hansard, and took the same approach across all four scripts.
\textbf{Despite our best efforts to capture all stage directions in this
list, because it had to be built manually, users should be aware that it
is possible that some stage directions were not separated onto their own
rows in the process. Further, it is important to note that because they
are not spoken aloud, stage directions do not represent speech
components in the same way that all other components such as
interjections and continuations do. However, they provide valuable
information about the inner-workings and structure of parliamentary
events. If the focus of the user's research does not require stage
directions, then this can be removed by filtering observations in
\texttt{name} equal to ``business start'', or ``stage direction''.}

@@

\textbf{To enhance the range of research questions which can be explored
with our data, we have created a supplementary file containing debate
topics and their corresponding page numbers for each sitting day in our
database. To extract these data, we wrote a script to parse debate and
sub-debate 1 information elements from each XML file in chronological
order using the XPath expression
``\texttt{//debate/debateinfo\ \textbar{}\ //subdebate.1/subdebateinfo}'',
and added a date variable with the date of each sitting day. Note that
in some cases there were multiple page number child nodes for the same
debate or sub-debate title, likely due to manual transcription error.
Upon manual inspection, we found that most often, the second page number
node contained the same page number as the first node, and sometimes the
second node contained a repeated debate title or a timestamp. Therefore,
we took the first available page number child-node for each debate or
sub-debate node to be the one we included in our dataset. After
summarizing, these topics can be added to the main text by joining, and
example code is provided in the README.}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{July 26, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, breakable, frame hidden, enhanced, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, formally known as
Hansard\textsuperscript{1}, plays a fundamental role in capturing the
history of political proceedings and facilitating the exploration of
valuable research questions. Originating in the British parliament, the
production of Hansard became tradition in many other Commonwealth
countries, such as Canada and Australia\textsuperscript{2}. Given the
content and magnitude of these records, they have significance,
particularly in the context of political science research. In the case
of Canada, the Hansard has been digitized for 1901 to
2019\textsuperscript{3}. Having a digitized version of Hansard enables
researchers to conduct text analysis and statistical modelling.
Following the lead of that project, in this paper we introduce a similar
database for Australia. This is composed of individual datasets for each
sitting day in the House of Representatives from 1998 to September 2022,
containing details on everything said in parliament in a form that can
be readily used by researchers. With the development of tools for
large-scale text analysis, this database will serve as a resource for
understanding political behaviour in Australia over time.

There are a wide variety of potential applications of this database. For
instance, within Australia there is considerable concern that there has
been a decline in the `quality' of public policy debate (however that
might be defined). Our dataset could be used to look at whether it is
really getting worse in particular ways, and if so, why. We might also
be interested in whether particular sub-populations are appropriately
represented in what is talked about in parliament. For instance, there
is often concern that regional areas are overlooked compared with
metropolitan areas. Again, our database could be used to examine whether
this has changed over time. We have developed our database in such a way
that it could be linked with similar databases from other countries
which would enable comparative analysis. For instance, we may be
interested in how the policy focus of a parliament changes given various
global events such as pandemics or wars. An international linkage
provides a comparison case where domestic issues are different while
international ones are common. As an example of enabling this linkage we
have included PartyFacts IDs in our database. This should make it
possible to link our database with other large parliamentary speech
collection projects, such as ParlaMint\textsuperscript{4},
ParlSpeech\textsuperscript{5}, ParlEE\textsuperscript{6}, and
MAPLE\textsuperscript{7}.

@@

At present, the Hansard format that is available on the Parliament of
Australia website is not easily accessible for large scale analysis. To
this point, various researchers have had to create their own databases
of usable, complete data based on content from the Australian Parliament
website. For instance, an online, easy to read database of Hansard from
1901 to 1980 using the XML files has been created\textsuperscript{9}.
These data can be navigated by year, parliament, people, and
bills\textsuperscript{9}. To make the Australian Parliamentary Handbook
more accessible, an \texttt{R} package which includes data on all MPs
from 1945 to 2019 has been created\textsuperscript{10}. Further, there
is the \texttt{AustralianPoliticians} \texttt{R} package, which contains
several datasets related to the political and biographical information
of Australian federal politicians who were active between 1901 and
2021\textsuperscript{11}. And finally, there has been examination of
speech and MP level data between 1990 and 2019 in
Australia\textsuperscript{12}. Like us they scrape the Hansard record
and link it with biographical data. The key difference is that our focus
is on the database itself, while they are focused on using a database
constructed from the same source to answer a particular question about
speaker time. This different focus leads to different emphasis and
approaches.

@@

This section is structured as follows. First, we provide an overview of
our approach to understanding and parsing an individual Hansard XML
document, which informed the scripts used to create our database. This
will be supplemented with an excerpt from a Hansard XML to provide a
visual example of its structure. Next we will explain the specific
differences between the scripts, and outline what structural changes
necessitated their separate development. We then provide details on the
methodological intricacies of three core components of Hansard
proceedings: Question Time, interjections, and stage directions.
Further, we discuss the script we developed to fill in remaining missing
details on the MP speaking, which each file in our database was passed
to after being parsed and cleaned. Finally, we review the supplementary
Hansard debate topics dataset and supplementary divisions dataset we
created to expand the versatility of our database.

@@

The outer-most node, also known as the parent node, is denoted
\texttt{\textless{}hansard\textgreater{}} and serves as a container for
the entire document. This parent node may have up to four child nodes,
where the first child node contains details on the specific sitting day.
Next, \texttt{\textless{}chamber.xscript\textgreater{}} contains all
proceedings of the Chamber,
\texttt{\textless{}fedchamb.xscript\textgreater{}} contains all
proceedings of the Federation Chamber, and
\texttt{\textless{}answers.to.questions\textgreater{}} contains Question
Time proceedings. The Federation Chamber does not meet on every sitting
day, so this child element is not present in every XML file. The use of
separate child nodes allows for the distinction of proceedings between
the Chamber and Federation Chamber. The structure of the
\texttt{\textless{}chamber.xscript\textgreater{}} and
\texttt{\textless{}fedchamb.xscript\textgreater{}} nodes are generally
the same, where the proceeding begins with
\texttt{\textless{}business.start\textgreater{}} which is followed by a
series of debates. Debate nodes can contain a
\texttt{\textless{}subdebate.1\textgreater{}} child node which has a
\texttt{\textless{}subdebate.2\textgreater{}} child node nested within
it. That said, sometimes \texttt{\textless{}subdebate.2\textgreater{}}
is not nested within \texttt{\textless{}subdebate.1\textgreater{}}. Each
of these three elements (i.e.~\texttt{\textless{}debate\textgreater{}},
\texttt{\textless{}subdebate.1\textgreater{}}, and
\texttt{\textless{}subdebate.2\textgreater{}}) as well as their
respective sub-elements contain important information on the topic of
discussion, who is speaking, and what is being said. The
\texttt{\textless{}speech\textgreater{}} node within each one contains
the bulk of the text associated with that debate or sub-debate. A
typical \texttt{\textless{}speech\textgreater{}} node begins with a
\texttt{\textless{}talk.start\textgreater{}} sub-node, providing
information on the MP whose turn it is to speak and the time of their
first statement. Unsurprisingly, speeches rarely go uninterrupted in
parliamentary debate settings --- they are often composed of a series of
interjections and continuations. These statements are categorized under
different sub-nodes depending on their nature, such as
\texttt{\textless{}interjection\textgreater{}} or
\texttt{\textless{}continuation\textgreater{}}. The final key component
of Hansard is Question Time, in which questions and answers are
classified as unique elements. More detail on the purpose and processing
of Question Time will \protect\hyperlink{sec-qa}{follow}.

@@

{\centering \includegraphics{xml1.jpg}

@@

The next step was to further develop our script to produce tidy data
sets, as defined and introduced by\textsuperscript{19}. These contain
all parsed text elements, where each statement is separated onto its own
row with details about the MP who is speaking, and rows are maintained
in chronological order. This first involved correcting the variable
classes and adding several indicator variables to differentiate where
statements came from, such as Chamber versus Federation Chamber or
\texttt{\textless{}subdebate.1\textgreater{}} versus
\texttt{\textless{}subdebate.2\textgreater{}}. The next key task stemmed
from the fact that the raw text data were not separated by each
statement when parsed. In other words, any interjections, comments made
by the Speaker or Deputy Speaker and continuations within an individual
speech were all parsed together as a single string. As such, the name,
name ID, electorate and party details were only provided for the person
whose turn it was to speak. There were many intricacies in the task of
splitting these speeches in a way that would be generalizable across
sitting days. Details on these are provided in the Interjections
\protect\hyperlink{sec-interject}{section} to follow.

@@

Once the script ran without error for a few recent years of Hansard, we
continued to work backwards until extensive changes in tree structure
made our script incompatible with parsing earlier XML files. The
earliest sitting day this first script can successfully parse is 14
August 2012. Before developing new scripts to parse earlier Hansard
documents, we prioritized cleaning and finalizing what we had been able
to parse. As such we continued building our script, fixing any problems
we noticed in the resulting datasets such as excess whitespace or
spacing issues, and splitting up any additional sections of the parsed
text onto separate rows where necessary. Specifically, we added a
section of our script to separate out general stage directions. More
information on this separation will be provided in the subsequent Stage
Directions \protect\hyperlink{sec-stage}{section}. After completing our
first script, it was formatted as a function which takes a single file
name argument and produces one CSV file containing data on all
proceedings from the given sitting day.

@@

As mentioned, we developed a total of four scripts to parse the
1998-2022 time frame of Hansard documents. Two main factors motivated us
to create four scripts as opposed to just one, the first being
structural variation in XML over time, and the second being improved
computational efficiency with separate scripts. While all four scripts
use the same general approach to parsing described in the Overview
\protect\hyperlink{sec-overview}{section} and produce the same CSV
structure, the first and second scripts use a different method of data
processing than the third and fourth scripts.

@@

{\centering \includegraphics[width=3.28125in,height=\textheight]{patternEX.jpg}

@@

We then added binary flags to differentiate between questions and
answers. To do this in the first and second scripts, we separately
re-parsed question and answer content using the XPath expressions
\texttt{"chamber.xscript//question"} and
\texttt{"chamber.xscript//answer"}, added the correct question and
answer flags accordingly, and then added those flags back to the main
dataframe based on exact text matches. For the third and fourth scripts,
we made use of the fact that the patterns preceding text transcribed
under a question node were stored separately from those transcribed
under an answer node. As a result, we could readily use those patterns
to flag questions and answers correctly based on which list of patterns
it belonged to. Sometimes, we identified questions which were
incorrectly transcribed under an answer node and vice-versa, in which
cases we manually corrected the question and answer flags. For instance,
we check for any statements flagged as questions which include the
phrase ``has provided the following answer to the honourable member's
question'', in which case we re-code that statement as an answer. It is
important to note, however, that because we identified and corrected for
these transcription errors manually as we discovered them, additional
flagging errors may exist which we did not catch. As such, users may
identify and should be wary of occasional incorrectly flagged questions
or answers in the data.

@@

As mentioned in the Script Differences
\protect\hyperlink{sec-diff}{section}, more recent years of Hansard XMLs
contain a series of child nodes which exist to capture the structure of
interruptions in that speech. Figure~\ref{fig-xml2} provides an example
of this, where the speech was interrupted by a comment from the Deputy
Speaker, and then the MP continued their speech. Looking at the element
names highlighted in blue, these child nodes do not contain the actual
text for the interjection or continuation --- this text is embedded
within the speech above it. However, as shown by the content highlighted
in pink in Figure~\ref{fig-xml2}, we were able to extract useful details
on the individual interjecting which we could use later. Making use of
this structure, we extracted names and information of all individuals
that were categorized within the XML as interjections. We stored this as
a dataframe called \texttt{"interject"}. We decided not to include this
data in our final database, as it is embedded in our resulting datasets
which have a flag for interjections.

@@

{\centering \includegraphics[width=3.59375in,height=\textheight]{xml2.jpg}

@@

\caption{\label{fig-xml2}Snapshot of XML structure with interjection and
continuation from 03 February 2021 Hansard}

@@

We then created lists using both the \texttt{interject} and
\texttt{main} dataframes to capture all the names of individuals who
spoke that day. We added the names of all MPs in a number of unique
formats, due to the frequent variation in how names are transcribed in
Hansard. When an MP interjects or continues a speech, the usual form of
their name is a title followed by their first name or first initial
and/or last name. There is also variation in the capitalization of these
names. Sometimes when someone's first name is included, only their last
name is capitalized, while sometimes their full name is capitalized, or
other times neither are capitalized. Another source of variation is in
individuals with more than one first name, as sometimes only their
initial first name is written, while other times their entire first name
is written. Additionally, some surnames have punctuation, and some
surnames have specific capitalization such as ``McCormack'', where even
in full capitalization, the first ``c'' remains lower case. This
variation demands careful consideration when writing regular expression
patterns. In these lists we also accounted for any general interjection
statements that were not attributed to an individual, such as ``An
opposition member interjecting-''.

@@

{\centering \includegraphics[width=4.66667in,height=\textheight]{lookup_ex.jpg}

@@

{\centering \includegraphics{interject_ex.jpg}

@@

Having developed a successful methodology for splitting interjections,
we used this to inform our general approach in the third and fourth
scripts. However, the difference in data cleaning used in these scripts
necessitated some departure from the original methodology. As discussed
in the Script Differences \protect\hyperlink{sec-diff}{section}, we used
string patterns extracted from
\texttt{\textless{}talk.start\textgreater{}} nodes to separate speeches.
As evident in Figure~\ref{fig-xml2},
\texttt{\textless{}talk.start\textgreater{}} nodes are nested within
\texttt{\textless{}interjection\textgreater{}} nodes, meaning that the
patterns of data from interjection statements were separated out in the
process. In other words, our approach to data cleaning in the third and
fourth scripts separated out interjections in the process. This meant
that we did not need to create lists of names and titles for which to
search in the text as we did before. However, we used the same list of
general interjection statements on which to separate as was used in the
first two scripts. We then did an additional check for statements that
may have not been separated due to how they were embedded in the XML,
and separated those out where needed. In particular, while most
statements were categorized in their own child node and hence captured
through pattern-based separation, some were not individually
categorized, and had to be split manually in this step.

@@

{\centering \includegraphics{pattern_lookup.jpg}

@@

When building our first scripts, one of the final components needed was
to separate general stage directions out from statements made by MPs.
Stage directions are general statements included in the transcript to
document happenings in parliament. Examples of stage directions are
``Bill read a second time'', ``Question agreed to'', or ``Debate
adjourned''. It was unclear to us from the XML and PDF who exactly these
statements were attributed to. For further clarification, we watched
portions of the video recording for some sitting days, and noticed that
while these statements are documented in Hansard, they are not
explicitly stated in parliament. For example, when the Deputy Speaker
says ``The question is that the bill be now read a second time'', MPs
vote, and if the majority is in favour, they proceed reading the bill
the second time. This vote and second reading is not explicitly
transcribed, rather what is written is: ``Question agreed to. Bill read
a second time''. For this reason, we filled the name variable for these
statements with ``stage direction''. Stage directions were not flagged
as interjections. These stage directions are not defined differently
from the regular debate speech in the XML, meaning we had to manually
create a list of stage directions to separate out of the speeches. We
built this list of stage directions as we worked backwards in parsing
Hansard, and took the same approach across all four scripts. Despite our
best efforts to capture all stage directions in this list, because it
had to be built manually, users should be aware that it is possible that
some stage directions were not separated onto their own rows in the
process. Further, it is important to note that because they are not
spoken aloud, stage directions do not represent speech components in the
same way that all other components such as interjections and
continuations do. However, they provide valuable information about the
inner-workings and structure of parliamentary events. If the focus of
the user's research does not require stage directions, then this can be
removed by filtering observations in \texttt{name} equal to ``business
start'', or ``stage direction''.

@@

To enhance the range of research questions which can be explored with
our data, we have created a supplementary file containing debate topics
and their corresponding page numbers for each sitting day in our
database. To extract these data, we wrote a script to parse debate and
sub-debate 1 information elements from each XML file in chronological
order using the XPath expression
``\texttt{//debate/debateinfo\ \textbar{}\ //subdebate.1/subdebateinfo}'',
and added a date variable with the date of each sitting day. Note that
in some cases there were multiple page number child nodes for the same
debate or sub-debate title, likely due to manual transcription error.
Upon manual inspection, we found that most often, the second page number
node contained the same page number as the first node, and sometimes the
second node contained a repeated debate title or a timestamp. Therefore,
we took the first available page number child-node for each debate or
sub-debate node to be the one we included in our dataset. After
summarizing, these topics can be added to the main text by joining, and
example code is provided in the README.
